Label object representation and manipulation with ITK

### 2008-08-04 article/Article.tex
fix computation of binary moments
darcs-hash:20080801131030-2fc9d-0fa0418b325eb53b2b771d477c6ba9b587275049.gz
fix the shamefully wrong equation and implement the most factorized formula for a bit much efficiency
darcs-hash:20080801133141-2fc9d-bf10214d99a93dc016bff59da14d0b7f5817cd5d.gz
enhance the doc a bit
darcs-hash:20080804104219-2fc9d-ea151a7d52f97f0072f55a9e1e8a539a3721ecb6.gz

The filter which are mainpulating binary images are often prefixed with the word
"Binary", to differenciate the grayscale version which don't have a prefix. It
seem to be a quite good practice which have been kept in that article.

@@

The label images are often used the represent the connected components of an
image. In this contribution, another representation has been chosen.

@@

The image is a collection of those objects, which also store some values of the image, like its size, its spacing, etc.

@@

No attribute are stored in this class, which can thus be seen as the base class
for the objects with attributes, or which can be used when no attributes
are required.

The {\em itk::LabelObject} class is templated and takes to required template parameters:
\begin{itemize}
  \item the type of the label,
  \item the dimension of the image.
\end{itemize}

Several subclasses are provided with that contribution, to cover the most common
usages of the label objects manipulation:
\begin{itemize}
  \item {\em itk::AttributeLabelObject} is able to store a generic attribute. It
is generic in the sense that its type is given in template parameter.
  \item {\em itk::ShapeLabelObject} contains numerous attribute related to the
shape of the label object. Computing the values of those attributes does not
require a feaure image.
  \item {\em itk::StatisticsLabelObject} contains numerous statistics about the
grey values of a feature image in the same place than the label object.
Computing the values of those attributes {\em does} require a feature image.
\end{itemize}

The classes {\em itk::ShapeLabelObject} and {\em itk::StatisticsLabelObject} have been
created to reduce the number of filters made to manipulate the attributes, and to make
the computation of all the set of attributes much efficient. In the early stage of
development, all the attributes were managed as in {\em itk::AttributeLabelObject}, and
a set of 8 classes made to manipulate a single attribute were provided, leading to a huge
number of classes.

@@

Both {\em itk::ShapeLabelObject} and {\em itk::StatisticsLabelObject} are templated classes.
They take the same template parameters than the {\em itk::LabelObject} class.
The 2 first template parameters of the {\em itk::AttributeLabelObject} class or the same
than the {\em itk::LabelObject} class. The third one is the attribute type.

@@

\begin{itemize}
  \item {\em Minimum} is the minimum value in the feature image for the object. Its type is
the feature image pixel type.
  \item {\em MinimumIndex} is the index position in the image where the first minimum was
found. Its type is{\em itk::Index< ImageDimension >}.
  \item {\em Maximum} is the maximum value in the feature image for the object. Its type is
the feature image pixel type.
  \item {\em MaximumIndex} is the index position in the image where the first maximum was
found. Its type is{\em itk::Index< ImageDimension >}.
  \item {\em Mean} is the mean of the pixel values in the object. Its type is {\em double}.
  \item {\em Sum} is the sum of all the pixel values in the objects. Its type is {\em double}.
  \item {\em Sigma} is the standard deviation of the pixels values in the objects. Its type
is {\em double}.
  \item {\em Variance} is the variance of the pixels values in the objects. Its type is
{\em double}.
  \item {\em Median} is the median of the pixels values in the obejct. Its type is
{\em double}
  \item {\em CenterOfGravity} is the center of gravity of the object. It type is
{\em itk::Point< double >}.
  \item {\em Kurtosis} is the kurtosis of the pixel values in the objects. Its type is
{\em double}.
  \item {\em Skewness} is the skewness of the pixel values in the objects. Its type is
{\em double}.
  \item {\em PrincipalMoments} contains the principal moments. Its type is
{\em itk::Vector< double, ImageDimension >}.
  \item {\em PrincipalAxes} contains the principal axes of the object. Its type is
{\em itk::Matrix< double, ImageDimension, ImageDimension >}.
  \item {\em Elongation} is the elongation of the shape, computed as the ratio
of the largest principal moment by the smallest principal moment. Its value is greater
or equal to $1$· Its type si {\em double}.
  \item {\em Histogram} is the histogram of the pixels covered by the label object
in the feature image. Its type is {\em itk::Histogram< double > *}.
\end{itemize}

@@

\begin{itemize}
  \item {\em itk::ShapeLabelMapFilter} to fill the
attributes of the {\em itk::ShapeLabelObject}s, 
  \item and {\em itk::ShapeLabelMapFilter} to fill the attributes of the {\em
itk::StatisticsLabelObject}s.
\end{itemize}

@@

\begin{itemize}
  \item An opening can be performed with the {\em
OpeningLabelMapFilter} classes. Those classes will remove all the
objects with an attribute value lower or greater than a given value.
Because we often can use some criteria  which have not been used during the segmentation
procedure, like the size of the object, the mean value of its pixels, etc., the attribute
opening is often a very efficient way to enhance a segmentation. For example, after
a thresholding of a grayscale image, the objects too small or too beg to be of interest
can be removed that way. The class {\em AttributeSelectionLabelMapFilter} and its subclass
{\em LabelSelectionLabelMapFilter} can be used to remove some objects based on their attribute
value, even if the attribute type has no ordering property.

@@

  \item The objects can be relabel, with the {\em
RelabelLabelMapFilter} classes. The order of the label is dependant
of the value of the attribute. Again, the user can choose to have the objects
with the highest attribute value in the first labels, or to have the objects
with the lowest attribute values in the first labels.

@@

\begin{eqnarray}
S_{i,j} = \begin{cases}
  \underset{L \in O}\sum \left( l_L.p_i.p_j \right)                & \text{if $i > 0$ and $j > 0$}, \\
  \underset{L \in O}\sum \left( l_L.p_i.\underset{p \in L}\sum p_0 \right)  & \text{if $i > 0$ and $j = 0$}, \\
  \underset{L \in O}\sum \left( l_L.p_j.\underset{p \in L}\sum p_0 \right)  & \text{if $i = 0$ and $j > 0$}, \\
  \underset{L \in O}\sum \underset{p \in L}\sum p_0^2            & \text{if $i = j = 0$}.
           \end{cases}
\end{eqnarray}

@@

\begin{eqnarray}
\sum_{p \in L} p_0^2  & = & \sum_{i_0=0}^{l_L-1} ( o_0 + s_0 i_0 )^2 \\ \nonumber
                      & = & \sum_{i_0=0}^{l_L-1} ( o_0^2 + s_0^2 i_0^2 + 2 o_0 i_0) \\ \nonumber
                      & = & l_L.o_0^2 + s_0^2\sum_{i_0=0}^{l_L-1} i_0^2 + 2 o_0 \sum_{i_0=0}^{l_L-1} i_0 \\ \nonumber
                      & = & l_L.o_0^2 + s_0^2 \left( \frac{(l_L-1)l_L(2l_L-1)}{6} \right) + 2 o_0 \left( \frac{(l_L-1)l_L}{2} \right) \\ \nonumber
                      & = & l_L\left( o_0^2 + (l_L-1)\left(\frac{s_0^2(2l_L-1)}{6}  + o_0 \right) \right)
\end{eqnarray}

Finally, $S_{i,j}$, used in the computation of the central moments, is computed as:
\begin{eqnarray}
S_{i,j} = \begin{cases}
  \underset{L \in O}\sum \left( l_L.p_i.p_j \right)                & \text{if $i > 0$ and $j > 0$}, \\
  \underset{L \in O}\sum \left( p_i.l_L^2 \left( o_0 + \frac{s_0(l_L-1)}{2} \right) \right) & \text{if $i > 0$ and $j = 0$}, \\
  \underset{L \in O}\sum \left( p_j.l_L^2 \left( o_0 + \frac{s_0(l_L-1)}{2} \right) \right) & \text{if $i = 0$ and $j > 0$}, \\
  \underset{L \in O}\sum \left( l_L\left( o_0^2 + (l_L-1)\left(\frac{s_0^2(2l_L-1)}{6}  + o_0 \right) \right) \right)            & \text{if $i = j = 0$}.
           \end{cases}
\end{eqnarray}

@@

\end{verbatim} \normalsize
then we can read the attribute values we're interested in. {\em itk::BinaryImageToLabelMapFilter}
produces consecutives labels, so a simple {for} loop will do the job.
\small \begin{verbatim}
  LabelMapType::Pointer labelMap = converter->GetOutput();
  for( unsigned int label=1; label<=labelMap->GetNumberOfLabelObjects(); label++ )
    {
    // we don't need a SmartPointer of the label object here, because the reference is kept in
    // in the label map.
    const LabelObjectType * labelObject = labelMap->GetLabelObject( label );
    std::cout << label << "\t" << labelObject->GetPhysicalSize() << "\t" << labelObject->GetCentroid() << std::endl;
    }

@@

Lets begin with the usual {\em import}s.
\small \begin{verbatim}
import itk, sys
itk.auto_progress()
\end{verbatim} \normalsize
Then declare the type we will use, as is {\em c++}.
\small \begin{verbatim}
Dimension = 2
PixelType = itk.UC
ImageType = itk.Image[ PixelType, Dimension ]

@@

LabelObjectType = itk.StatisticsLabelObject[itk.UL, Dimension]
LabelMapType = itk.LabelMap[LabelObjectType]
\end{verbatim} \normalsize
read the image of the nucleus
\small \begin{verbatim}
nuclei = itk.ImageFileReader[ImageType].New(FileName="images/noyaux.png")
\end{verbatim} \normalsize
perform a simple binarization. Note that the Otsu filter does not use the same convention as usual: the white part is outside.
\small \begin{verbatim}
otsu = itk.OtsuThresholdImageFilter[ImageType, ImageType].New(nuclei, OutsideValue=255,
    InsideValue=0)
\end{verbatim} \normalsize
The nuclei are not separated. We split them with a watershed.
\small \begin{verbatim}
maurer = itk.SignedMaurerDistanceMapImageFilter[ImageType, DistanceImageType].New(otsu)
watershed = itk.MorphologicalWatershedImageFilter[DistanceImageType, ImageType].New(maurer,
    Level=60, MarkWatershedLine=False)
mask = itk.MaskImageFilter[ImageType, ImageType, ImageType].New(watershed, otsu)
\end{verbatim} \normalsize
And now switch to the label collection representation
\small \begin{verbatim}
label = itk.LabelImageToLabelMapFilter[ImageType, LabelMapType].New(mask)
\end{verbatim} \normalsize
compute the attribute values
\small \begin{verbatim}
stats = itk.StatisticsLabelMapFilter[LabelMapType, ImageType].New(label, nuclei)
\end{verbatim} \normalsize
drop the objects too small to be a nucleus, and the ones on the border
\small \begin{verbatim}
size = itk.ShapeOpeningLabelMapFilter[LabelMapType].New(stats,Attribute='Size',
    Lambda=100)
border = itk.ShapeOpeningLabelMapFilter[LabelMapType].New(size, Attribute='SizeOnBorder',
    Lambda=10, ReverseOrdering=True)
\end{verbatim} \normalsize
Reoder the labels. The objects with the highest mean are the first ones.
\small \begin{verbatim}
relabel = itk.StatisticsRelabelLabelMapFilter[LabelMapType].New(border, Attribute='Mean')
\end{verbatim} \normalsize
for visual validation:
\small \begin{verbatim}
labelNuclei = itk.LabelMapToLabelImageFilter[LabelMapType, ImageType].New(relabel)
overlay = itk.LabelOverlayImageFilter[ImageType, ImageType, RGBImageType].New(nuclei,
    labelNuclei, UseBackground=True)
itk.write(overlay, "nuclei-overlay.png")
\end{verbatim} \normalsize

@@

Now, the spots:
\small \begin{verbatim}
spots = itk.ImageFileReader[ImageType].New(FileName="images/spots.png")
\end{verbatim} \normalsize
Mask the spot image to keep only the nucleus zone. The rest of the image is cropped, excepted a border of 2 pixels
\small \begin{verbatim}
maskSpots = itk.LabelMapMaskImageFilter[LabelMapType, ImageType].New(relabel, spots, Label=1,
    Crop=True, CropBorder=2)
\end{verbatim} \normalsize
A simple thresholding:
\small \begin{verbatim}
th = itk.BinaryThresholdImageFilter[ImageType, ImageType].New(maskSpots, LowerThreshold=110)
\end{verbatim} \normalsize
Now swith to the label collection representation, and compute the attribute values. This time, the input image is not a label image, but a binary one.
\small \begin{verbatim}
slabel = itk.BinaryImageToLabelMapFilter[ImageType, LabelMapType].New(th)
sstats = itk.StatisticsLabelMapFilter[LabelMapType, ImageType].New(slabel, nuclei)
\end{verbatim} \normalsize
we know there are for spots in the nubleus, so keep the 4 biggest spots. The other attribute are also usable - we may have chosen to keep the 4 brightest spots for example.
\small \begin{verbatim}
skeep = itk.ShapeKeepNObjectsLabelMapFilter[LabelMapType].New(sstats, Attribute='Size',
    NumberOfObjects=4)
\end{verbatim} \normalsize
Reoder the labels. The bigger objects first.
\small \begin{verbatim}
srelabel = itk.StatisticsRelabelLabelMapFilter[LabelMapType].New(skeep, Attribute='Size')
\end{verbatim} \normalsize
Finally, display the values we are interested in:
\begin{itemize}
  \item the nucleus number,
  \item the spot position,
  \item the mean value in the nucleus in the spot zone.
\end{itemize}

@@

The {\em itk::BinaryImageToLabelMapFilter} class should be threaded to get the best of that filter on multiprocessors systems.

>>>>

The filters which are manipulating binary images are often prefixed with the word
"Binary", to differenciate the grayscale versions which don't have a prefix. It
seem to be a quite good practice which have been kept in that article.

@@

The label images are often used to represent the connected components of an
image. In this contribution, another representation has been chosen.

@@

The image is a collection of those objects, and it also store some values of the image,
like its size, its spacing, etc.

@@

No attribute -- excepted the label -- are stored in this class, which can thus be seen as the base class
for the objects with attributes, or which can be used when no attributes
are required.

The {\em itk::LabelObject} class is templated and takes two required template parameters:
\begin{itemize}
  \item the type of the label;
  \item the dimension of the image.
\end{itemize}

Several subclasses are provided with that contribution, to cover the most common
usages of the label objects manipulation:
\begin{itemize}
  \item {\em itk::AttributeLabelObject} is able to store a generic attribute. It
is generic in the sense that its type is given in template parameter.
  \item {\em itk::ShapeLabelObject} contains numerous attribute related to the
shape of the label object. Computing the values of those attributes does not
require a feature image.
  \item {\em itk::StatisticsLabelObject} contains numerous statistics about the
grey values of a feature image in the same place than the label object.
Computing the values of those attributes {\em does} require a feature image.
\end{itemize}

The classes {\em itk::ShapeLabelObject} and {\em itk::StatisticsLabelObject} have been
created to reduce the number of filters made to manipulate the attributes, and to make
the computation of all the set of attributes much efficient\footnote{In the early stage of
development, all the attributes were managed as in {\em itk::AttributeLabelObject}, and
a set of 8 classes made to manipulate a single attribute were provided, leading to a huge
number of classes.}.

@@

The position in the images are given in index position when the position is the exact position
of a pixel (for example, the position of the maximum value in the feature image) or in physical
position when the position is given at a subpixel resolution (for example, the centroid). In
both case, the position can easily be converted to the other representation with the 
{\em itk::LabelMap::TransformPhysicalPointToIndex()} and {\em itk::LabelMap::TransformIndexToPhysicalPoint()}
methods.

Both {\em itk::ShapeLabelObject} and {\em itk::StatisticsLabelObject} are templated classes.
They take the same template parameters than the {\em itk::LabelObject} class.
The two first template parameters of the {\em itk::AttributeLabelObject} class or the same
than the ones of the{\em itk::LabelObject} class. The third one is the attribute type.

@@

\begin{itemize}
  \item {\em Minimum} is the minimum value in the feature image for the object. Its type is
the feature image pixel type.
  \item {\em MinimumIndex} is the index position in the image where the first minimum was
found. Its type is{\em itk::Index< ImageDimension >}.
  \item {\em Maximum} is the maximum value in the feature image for the object. Its type is
the feature image pixel type.
  \item {\em MaximumIndex} is the index position in the image where the first maximum was
found. Its type is{\em itk::Index< ImageDimension >}.
  \item {\em Mean} is the mean of the pixel values in the object. Its type is {\em double}.
  \item {\em Sum} is the sum of all the pixel values in the objects. Its type is {\em double}.
  \item {\em Sigma} is the standard deviation of the pixels values in the objects. Its type
is {\em double}.
  \item {\em Variance} is the variance of the pixels values in the objects. Its type is
{\em double}.
  \item {\em Median} is the median of the pixels values in the obejct. Its type is
{\em double}
  \item {\em CenterOfGravity} is the center of gravity of the object. Its type is
{\em itk::Point< double >}.
  \item {\em Kurtosis} is the kurtosis of the pixel values in the objects. Its type is
{\em double}.
  \item {\em Skewness} is the skewness of the pixel values in the objects. Its type is
{\em double}.
  \item {\em PrincipalMoments} contains the principal moments. Its type is
{\em itk::Vector< double, ImageDimension >}.
  \item {\em PrincipalAxes} contains the principal axes of the object. Its type is
{\em itk::Matrix< double, ImageDimension, ImageDimension >}.
  \item {\em Elongation} is the elongation of the shape, computed as the ratio
of the largest principal moment by the smallest principal moment. Its value is greater
or equal to $1$· Its type si {\em double}.
  \item {\em Histogram} is the histogram of the pixels covered by the label object
in the feature image. Its type is {\em itk::Histogram< double > *}.
\end{itemize}

@@

\begin{itemize}
  \item {\em itk::ShapeLabelMapFilter} to fill the
attributes of the {\em itk::ShapeLabelObject}s, 
  \item and {\em itk::StatisticsLabelMapFilter} to fill the attributes of the {\em
itk::StatisticsLabelObject}s.
\end{itemize}

@@

\begin{itemize}
  \item An opening can be performed with the {\em
OpeningLabelMapFilter} classes. Those classes will remove all the
objects with an attribute value lower or greater than a given value.
Because we often can use some criteria  which have not been used during the segmentation
procedure, like the size of the object, the mean value of its pixels, etc., the attribute
opening is often a very efficient way to enhance a segmentation. For example, after
a thresholding of a grayscale image, the objects too small or too big to be of interest
can be removed that way. The class {\em AttributeSelectionLabelMapFilter} and its subclass
{\em LabelSelectionLabelMapFilter} can be used to remove some objects based on their attribute
value, even if the attribute type has no ordering property.

@@

  \item The objects can be relabeled, with the {\em
RelabelLabelMapFilter} classes. The order of the label is dependant
of the value of the attribute. Again, the user can choose to have the objects
with the highest attribute value in the first labels, or to have the objects
with the lowest attribute values in the first labels.

@@

\begin{eqnarray}
S_{i,j} = \begin{cases}
  \underset{L \in O}\sum \left( l_L.p_i.p_j \right)                & \text{if $i > 0$ and $j > 0$}, \\
  \underset{L \in O}\sum \left( p_i.\underset{p \in L}\sum p_0 \right)  & \text{if $i > 0$ and $j = 0$}, \\
  \underset{L \in O}\sum \left( p_j.\underset{p \in L}\sum p_0 \right)  & \text{if $i = 0$ and $j > 0$}, \\
  \underset{L \in O}\sum \underset{p \in L}\sum p_0^2            & \text{if $i = j = 0$}.
           \end{cases}
\end{eqnarray}

@@

\begin{eqnarray}
\sum_{p \in L} p_0^2  & = & \sum_{i_0=0}^{l_L-1} ( o_0 + s_0 i_0 )^2 \\ \nonumber
                      & = & \sum_{i_0=0}^{l_L-1} ( o_0^2 + s_0^2 i_0^2 + 2 o_0 s_0 i_0) \\ \nonumber
                      & = & l_L.o_0^2 + s_0^2\sum_{i_0=0}^{l_L-1} i_0^2 + 2 o_0 s_0 \sum_{i_0=0}^{l_L-1} i_0 \\ \nonumber
                      & = & l_L.o_0^2 + s_0^2 \left( \frac{(l_L-1)l_L(2l_L-1)}{6} \right) + 2 o_0 s_0 \left( \frac{(l_L-1)l_L}{2} \right) \\ \nonumber
                      & = & l_L\left( o_0^2 + s_0 (l_L-1)\left(\frac{s_0(2l_L-1)}{6}  + o_0 \right) \right)
\end{eqnarray}

Finally, $S_{i,j}$, used in the computation of the central moments, is computed as:
\begin{eqnarray}
S_{i,j} = \begin{cases}
  \underset{L \in O}\sum \left( l_L.p_i.p_j \right)                & \text{if $i > 0$ and $j > 0$}, \\
  \underset{L \in O}\sum \left( p_i.l_L \left( o_0 + \frac{s_0(l_L-1)}{2} \right) \right) & \text{if $i > 0$ and $j = 0$}, \\
  \underset{L \in O}\sum \left( p_j.l_L \left( o_0 + \frac{s_0(l_L-1)}{2} \right) \right) & \text{if $i = 0$ and $j > 0$}, \\
  \underset{L \in O}\sum \left( l_L\left( o_0^2 + s_0 (l_L-1)\left(\frac{s_0(2l_L-1)}{6}  + o_0 \right) \right) \right)            & \text{if $i = j = 0$}.
           \end{cases}
\end{eqnarray}

@@

\end{verbatim} \normalsize
then we can read the attribute values we're interested in. {\em itk::BinaryImageToLabelMapFilter}
produces consecutives labels, so a simple {\em for} loop will do the job.
\small \begin{verbatim}
  LabelMapType::Pointer labelMap = converter->GetOutput();
  for( unsigned int label=1; label<=labelMap->GetNumberOfLabelObjects(); label++ )
    {
    // we don't need a SmartPointer of the label object here, because the reference is kept in
    // in the label map.
    const LabelObjectType * labelObject = labelMap->GetLabelObject( label );
    std::cout << label << "\t" << labelObject->GetPhysicalSize() << "\t" << labelObject->GetCentroid() << std::endl;
    }

@@

Lets begin with the usual {\em import}s.
\small \begin{verbatim}
import itk, sys
itk.auto_progress()
\end{verbatim} \normalsize
Then declare the type we will use, as in {\em C++}.
\small \begin{verbatim}
Dimension = 2
PixelType = itk.UC
ImageType = itk.Image[ PixelType, Dimension ]

@@

LabelObjectType = itk.StatisticsLabelObject[itk.UL, Dimension]
LabelMapType = itk.LabelMap[LabelObjectType]
\end{verbatim} \normalsize
read the image of the nucleus
\small \begin{verbatim}
nuclei = itk.ImageFileReader[ImageType].New(FileName="images/noyaux.png")
\end{verbatim} \normalsize
perform a simple binarization. Note that the Otsu filter does not use the same convention as usual: the white part is outside.
\small \begin{verbatim}
otsu = itk.OtsuThresholdImageFilter[ImageType, ImageType].New(nuclei, OutsideValue=255,
    InsideValue=0)
\end{verbatim} \normalsize
The nuclei are not separated. We split them with a watershed.
\small \begin{verbatim}
maurer = itk.SignedMaurerDistanceMapImageFilter[ImageType, DistanceImageType].New(otsu)
watershed = itk.MorphologicalWatershedImageFilter[DistanceImageType, ImageType].New(maurer,
    Level=60, MarkWatershedLine=False)
mask = itk.MaskImageFilter[ImageType, ImageType, ImageType].New(watershed, otsu)
\end{verbatim} \normalsize
And now switch to the label map representation, and compute the attribute values
\small \begin{verbatim}
stats = itk.LabelImageToStatisticsLabelMapFilter[ImageType, ImageType, LabelMapType].New(mask,
    nuclei)
\end{verbatim} \normalsize
drop the objects too small to be a nucleus, and the ones on the border
\small \begin{verbatim}
size = itk.ShapeOpeningLabelMapFilter[LabelMapType].New(stats,Attribute='Size',
    Lambda=100)
border = itk.ShapeOpeningLabelMapFilter[LabelMapType].New(size, Attribute='SizeOnBorder',
    Lambda=10, ReverseOrdering=True)
\end{verbatim} \normalsize
Reoder the labels. The objects with the highest mean are the first ones.
\small \begin{verbatim}
relabel = itk.StatisticsRelabelLabelMapFilter[LabelMapType].New(border, Attribute='Mean')
\end{verbatim} \normalsize
for visual validation:
\small \begin{verbatim}
overlay = itk.LabelMapOverlayImageFilter[LabelMapType, ImageType, RGBImageType].New(relabel,
    nuclei)
itk.write(overlay, "nuclei-overlay.png")
\end{verbatim} \normalsize

@@

Now, the spots:
\small \begin{verbatim}
spots = itk.ImageFileReader[ImageType].New(FileName="images/spots.png")
\end{verbatim} \normalsize
Mask the spot image to keep only the nucleus zone. The rest of the image is cropped, excepted a border of 2 pixels
\small \begin{verbatim}
maskSpots = itk.LabelMapMaskImageFilter[LabelMapType, ImageType].New(relabel, spots, Label=1,
    Crop=True, CropBorder=2)
\end{verbatim} \normalsize
A simple thresholding:
\small \begin{verbatim}
th = itk.BinaryThresholdImageFilter[ImageType, ImageType].New(maskSpots, LowerThreshold=110)
\end{verbatim} \normalsize
Now swith to the label map representation, and compute the attribute values. This time, the input image is not a label image, but a binary one.
\small \begin{verbatim}
sstats = itk.BinaryImageToStatisticsLabelMapFilter[ImageType, ImageType, LabelMapType].New(th,
    nuclei)
\end{verbatim} \normalsize
we know there are 4 spots in the nubleus, so keep the 4 biggest spots. The other attributes are also usable - we may have chosen to keep the 4 brightest spots for example.
\small \begin{verbatim}
skeep = itk.ShapeKeepNObjectsLabelMapFilter[LabelMapType].New(sstats, Attribute='Size',
    NumberOfObjects=4)
\end{verbatim} \normalsize
Reoder the labels. The bigger objects first.
\small \begin{verbatim}
srelabel = itk.StatisticsRelabelLabelMapFilter[LabelMapType].New(skeep, Attribute='Size')
\end{verbatim} \normalsize
Finally, display the values we are interested in:
\begin{itemize}
  \item the nucleus number,
  \item the spot position,
  \item the mean value in the nucleus in the spot zone.
\end{itemize}

@@
